### 2024-07-21 data-visualization.qmd
20240721 - fix error

```{r}
#| label: fig-rushYPCperSeasonByAge
#| fig-cap: "NFL Rushing Yards Per Carry Per Season by Player Age"

@@

```{r}
#| label: fig-rushYPCperSeasonByAge
#| fig-cap: "NFL Rushing Yards Per Carry Per Season by Player Age"

@@

```{r}
#| label: fig-rushEPAperSeasonByAge
#| fig-cap: "NFL Rushing Expected Points Added (EPA) per Season by Player Age"

@@

```{r}
#| label: fig-rushEPAperSeasonByAge
#| fig-cap: "NFL Rushing Expected Points Added (EPA) per Season by Player Age"

@@

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2023 NFL Offensive and Defensive EPA per Play"

>>>>

Rushing yards per carry over the course of the season is depicted as a function of the Running Back's age in @fig-rushYPCperSeasonByAge.

```{r}
#| label: fig-rushYPCperSeasonByAge
#| fig-cap: "Rushing Yards Per Carry (Season) by Player Age."

@@

Rushing yards per carry over the course of the season is depicted as a function of the Running Back's age in @fig-rushYPCperSeasonByAgePDF.

```{r}
#| label: fig-rushYPCperSeasonByAgePDF
#| fig-cap: "NFL Rushing Yards Per Carry Per Season by Player Age."

@@

Rushing expected points added (EPA) over the course of the season is depicted as a function of the Running Back's age in @fig-rushEPAperSeasonByAge.

```{r}
#| label: fig-rushEPAperSeasonByAge
#| fig-cap: "Rushing Expected Points Added (Season) by Player Age."

@@

Rushing expected points added (EPA) over the course of the season is depicted as a function of the Running Back's age in @fig-rushEPAperSeasonByAgePDF.

```{r}
#| label: fig-rushEPAperSeasonByAgePDF
#| fig-cap: "NFL Rushing Expected Points Added (EPA) per Season by Player Age."

@@

Defensive EPA per play during the 2023 NFL season is depicted as a function of offensive EPA per play in @fig-plotDefOffEPA.

```{r}
#| label: fig-plotDefOffEPA
#| fig-cap: "2023 NFL Offensive and Defensive EPA Per Play."
